High-Performance Data Analysis on JANUS using Apache Spark

### 2013-12-18 paper.tex
pixel

We have tested the scalability of Spark system on distributed Grep program and we still want to see whether for iterative algorithms, it’s also scalable by looking at the time as the number of nodes increases.\\

>>>>

We have tested the scalability of Spark system on distributed Grep program and we still want to see whether for iterative algorithms, it's also scalable by looking at the time as the number of nodes increases.\\
